Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
fix missing conflict

In this paper, we first study a framework of assembling multiple small binary classifiers into one that performs complicated classification tasks.
Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.

@@

Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$ in the orange box, no two subclasses with different labels share the same encoding, and therefore it certifies the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ in the blue box already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

\subsection{The Heuristic Search Algorithm}
\label{sec:assembly-algorithm}
Based on the encoding method, we propose a search algorithm based on greedy heuristics in Algorithm~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.

@@

\section{Experiments}
\label{sec:experiments}
\subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
\paragraph{Clusters.} We perform K-Means on the CDRP control gates of each sample. 
For VGGNet, we generate $1.5$ clusters per class.
Then, we get $14$ clusters from $5$ classes, among which $7$ clusters are from VGG16-C and $7$ clusters from VGG16-D.

@@

\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifier. Each classifier judges whether the test sample should in the corresponding cluster. 
From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.

\begin{table}[h]
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline
	\end{tabular}
\end{table}

Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
As a result, each classifier only has $10\%$ parameters of the original full network.

@@

We train each classifier with $1500$ iterations with a batch size $200$. 
The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
We only train the pruned model i.e. weights of the pruned channels will remain zero.
After finetune, most of the classifiers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers are shown in Table~\ref{tab:classifier-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[h]
    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifier-accuracy}
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Classifier ID & 3 & 4 & 1 & 2 \\
	\hline
	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\end{tabular}
\end{table}

@@

Actually, we can determine the class uniquely with the prefix of encodings. 
For instance, if the result of classifier-3 is $0$, we don't need to take other classifiers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}

The corresponding encoding of each class label is shown in Table~\ref{tab:encoding-and-accuarcy}. We can determine the class label with this encoding, the accuracy of which is also shown in Table~\ref{tab:encoding-and-accuarcy}.

\begin{table}[h]
    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 &\\
	\hline
	\end{tabular}
\end{table}

>>>>

In this paper, we first study a framework of assembling multiple small binary classifiers into one that performs complicated classification tasks.
\Cref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.

@@

\Cref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in \Cref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$ in the orange box, no two subclasses with different labels share the same encoding, and therefore it certifies the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ in the blue box already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

\subsection{The Heuristic Search Algorithm}
\label{sec:assembly-algorithm}
Based on the encoding method, we propose a search algorithm based on greedy heuristics in \cref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.

@@

\section{Experiments}
\label{sec:experiments}
\subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
In this section, we perform K-Means on the CDRP control gates of each sample. For each cluster, we get a binary-classifier to determine whether the test sample should be in the cluster. Then, we fine tune each classifier in the CIFAR-100 dataset.

\paragraph{Clusters.} For VGGNet, we generate $1.5$ clusters per class.
Then, we get $14$ clusters from $5$ classes, among which $7$ clusters are from VGG16-C and $7$ clusters from VGG16-D.

@@

\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifier. Each classifier judges whether the test sample should in the corresponding cluster. 
From \cref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in \cref{tab:cluster_label}.

\begin{table}[h]
	\caption{Corresponding Class Labels of Each Cluster}
	\label{tab:cluster_label}
	\begin{tabular}{|c|c|c|}
	\hline
	\multirow{2}{*}{Classifier} &\multicolumn{2}{c|}{Possible Class Labels}\\
	\cline{2-3}
	& In (0) & Not in (1)\\
	\hline
	classifier-0,6 & 4 & 0,1,2,3,4,5\\
	classifier-1 & 1 & 0,2,3,4,5\\
	classifier-2 & 2 & 0,1,3,4,5\\
	classifier-3 & 0 & 1,2,3,4,5\\
	classifier-4 & 3 & 0,1,2,4,5\\
	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
	classifier-9 & 2,3,4 & 0,1,5\\ 
	classifier-8,13 & 0 & 1,2,3,4,5\\
	classifier-10,12 & 1 & 0,1,2,3,4,5\\
	classifier-11 & 3 & 0,1,2,3,4,5\\
	\hline
	\end{tabular}
\end{table}

Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $pr$ i.e. if $pr=0.9$, $90\%$ of channels in all layers are pruned. 
As a result, each classifier only has $10\%$ parameters of the original full network.

@@

We train each classifier with $1500$ iterations with a batch size $200$. 
The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
We only train the pruned model i.e. weights of the pruned channels will remain zero.
With a prune ratio $pr\leq0.9$, most of the classifiers can reach an accuracy more than 80\% after finetune, which is much higher than the overall accuracy of the original full network.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
In this section, we implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers. According to the 0/1 result of each classifier, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.

\paragraph{Fusion}We implement \cref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this \cref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers with different prune ratio is shown in \cref{tab:classifier-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[h]

    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifier-accuracy}
	\begin{tabular}{ccccc}
	\toprule
	Classifier ID & 3 & 4 & 1 & 2 \\
	\midrule
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
	\bottomrule
	\end{tabular}
\end{table}

@@

Actually, we can determine the class uniquely with the prefix of encodings. 
For instance, if the result of classifier-3 is $0$, we don't need to take other classifiers into consideration since the only class $0$ is possible in cluster-3 according to \cref{tab:cluster_label}

The corresponding encoding of each class label is shown in \cref{tab:encoding-and-accuarcy}. 
We can determine the class label with this encoding, the accuracy of which is also shown in \cref{tab:encoding-and-accuarcy}.

\begin{table}[h]

    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{ccccccc}
	\toprule
	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\midrule
	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\

	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\
	\bottomrule

	\end{tabular}
\end{table}

From \cref{tab:encoding-and-accuarcy}, we find the overall accuracy is quite high if prune ratio $pr\leq0.9$ while the accuracy drops dramatically when $pr=0.95$ since we prune too much channels or even destroy the connectivity of the network. 
When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.
Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency. When $pr=0.9$, we can inference with the $4$ classifiers in parallel, which can save about $90\%$ computing consumption on a single device.
